---
title: "Sign commits (GPG)"
author: "Ildiko Czeller"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sign commits (GPG)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(ropsec)
```

[Installation instructions](https://github.com/jeroen/gpg)

[General info on GPG](https://cran.r-project.org/web/packages/gpg/vignettes/intro.html)

## Default use-case

Run this function once to generate a new key and set it to sign all future commits in all repositories.

```{r eval=FALSE}
sign_commits_with_key(name = "John Doe", email = "johndoe@example.com")
```

```{r echo = FALSE}
message("`John Doe` (as provided) and
`johndoe@example.com` (as provided)
will be used to generate a new gpg key.")
cat("Please enter password for new gpg key (can be blank): ********\n")
cat("Do you want to sign all future commits with `ABCDEFGHIJKLMNOP` in all repositories?

1: Yes
2: Not now
3: Absolutely not
Selection: 1")
"ABCDEFGHIJKLMNOP"
```



## Existing key

### provide key id

```{r eval=FALSE}
sign_commits_with_key(key = "ABCDEFGHIJKLMNOP")
```

```{r echo = FALSE}
message("Do you want to sign all future commits with `ABCDEFGHIJKLMNOP` in all repositories?

1: Absolutely not
2: Not now
3: Yes

Selection: 1")
"ABCDEFGHIJKLMNOP"
```

### find based on user name and/or email

```{r eval=FALSE}
sign_commits_with_key(name = "John Doe")
```

```{r echo=FALSE}
message("Existing key found: ABCDEFGHIJKLMNOP.
Corresponding email: johndoe@example.com (based on local git config).

Do you want to sign all future commits with `ABCDEFGHIJKLMNOP` in all repositories?

1: Yes
2: Absolutely not
3: Not now

Selection: 1")
"ABCDEFGHIJKLMNOP"
```

```{r eval=FALSE}
sign_commits_with_key(email = "johndoe@example.com")
```

```{r echo=FALSE}
message("Existing key found: ABCDEFGHIJKLMNOP.
Corresponding email: johndoe@example.com (as provided).

Do you want to sign all future commits with `ABCDEFGHIJKLMNOP` in all repositories?

1: Yes
2: Not now
3: Absolutely not

Selection: 1")
"ABCDEFGHIJKLMNOP"
```


## Use different keys in different repositories.

One common use-case is to have a personal and a work email as well and you use git with both of them. At the first time you want to use them, generate a key and set to use it in the repository.

Later, for convenience the appropriate key can be identified based on email as well or if the local git config is set you can even rely on that.