---
title: "Sign commits (GPG)"
author: "Ildiko Czeller"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sign commits (GPG)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


It is good practice to sign your commits so that your commits can be verified as certainly made by you and not by someone impersonating you.

One technology to enable this is [GPG](https://gnupg.org/) for which and R interface is created by [Jeroen Ooms](https://github.com/jeroen). The current package provides helper functions and aim to ease the process as much as possible.

First, make sure that dependencies are installed:

[Installation instructions](https://github.com/jeroen/gpg)

If you are interested in background, 
[general info on GPG](https://cran.r-project.org/web/packages/gpg/vignettes/intro.html) is highly recommended.

```{r}
library(ropsec)
```

## Default use-case

Run this function once to generate a new key and set it to sign all future commits in all repositories.

```{r eval=FALSE}
sign_commits_with_key(name = "John Doe", email = "johndoe@example.com")
```

```{r echo = FALSE}
message("`John Doe` (as provided) and
`johndoe@example.com` (as provided)
will be used to generate a new gpg key.")
cat("Please enter password for new gpg key (can be blank): ********\n")
cat("Do you want to sign all future commits with `ABCDEFGHIJKLMNOP` in all repositories?

1: Yes
2: Not now
3: Absolutely not
Selection: 1")
"ABCDEFGHIJKLMNOP"
```



## Existing key

### provide key id

```{r eval=FALSE}
sign_commits_with_key(key = "ABCDEFGHIJKLMNOP")
```

```{r echo = FALSE}
message("Do you want to sign all future commits with `ABCDEFGHIJKLMNOP` in all repositories?

1: Absolutely not
2: Not now
3: Yes

Selection: 1")
"ABCDEFGHIJKLMNOP"
```

### find based on user name and/or email

```{r eval=FALSE}
sign_commits_with_key(name = "John Doe")
```

```{r echo=FALSE}
message("Existing key found: ABCDEFGHIJKLMNOP.
Corresponding email: johndoe@example.com (based on local git config).

Do you want to sign all future commits with `ABCDEFGHIJKLMNOP` in all repositories?

1: Yes
2: Absolutely not
3: Not now

Selection: 1")
"ABCDEFGHIJKLMNOP"
```

```{r eval=FALSE}
sign_commits_with_key(email = "johndoe@example.com")
```

```{r echo=FALSE}
message("Existing key found: ABCDEFGHIJKLMNOP.
Corresponding email: johndoe@example.com (as provided).

Do you want to sign all future commits with `ABCDEFGHIJKLMNOP` in all repositories?

1: Yes
2: Not now
3: Absolutely not

Selection: 1")
"ABCDEFGHIJKLMNOP"
```


## Use different keys in different repositories.

One common use-case is to have a personal and a work email as well and you use git with both of them. At the first time you want to use them, generate a key and set to use it in the repository.

In a personal git repository:

```{r eval=FALSE}
sign_commits_with_key(name = "John Doe", email = "jd@personal.com", global = FALSE)
```

In a work-related git repository:

```{r eval=FALSE}
sign_commits_with_key(name = "John Doe", email = "jd@company.com", global = FALSE)
```

Later, for convenience the appropriate key can be identified based on email as well or if the local git config is set you can even rely on that.

In another work-related repository:

```{r eval=FALSE}
sign_commits_with_key(email = "jd@company.com", global = FALSE)
```

In yet another work-related repository:

```{bash eval=FALSE}
git config user.email jd@company.com
```

```{r eval=FALSE}
sign_commits_with_key(global = FALSE)
```

```{r echo=FALSE}
cat("Existing key found: 1234561234561234.
Corresponding email: jd@company.com (based on local git config).

Do you want to sign all future commits with `1234561234561234` in this repository?

1: Yes
2: Absolutely not
3: Not now

Selection: 1")
"1234561234561234"
```


You may choose to set one of them globally which thus will be the default key to use in a repository where the repository level configs are not set to a different value.